\Huge \textbf{Hybrid rendering}\\ \huge using Radeon Rays

### 2018-11-03 Paper/Paper_BillietStijn_RadeonRays.tex
Fixed small typo, on to case study

As touched earlier deferred rendering fills the off screen render buffers (g-buffers) with scene information in its first pass. This effectively enables us to do rendering after the fact by then using that information to construct everything we need to apply our lighting.\newline\par

>>>>

As touched earlier deferred rendering fills the off screen render buffers (g-buffers) with scene information in its first pass. This effectively enables us to do lighting after the fact by then using that information to construct everything we need to apply our lighting.\newline\par
